\vfill LiteCrypto

### 2014-12-12 paper/paper.tex
More revisions

\vfill  %in combination with \newpage this forces the abstract to the bottom of the page
\begin{abstract}
As satellite communication becomes more accessible with the introduction of CubeSats, the need for authenticated and encrypted communication become necessary to protect against attackers. We have developed a lightweight, open-source cryptographic library suitable for satellites, specfically CubeSats, based on the NaCl and TweetNaCl libraries. The library, LiteCrypto, includes authentication, encryption, and authenticated encryption for IPv4 packets under symmetric keys.

@@

Dr. Bellardo has discussed with our team that the future of CubeSat is to allow them to move in space. However, their current communications from home base to the satellite is encrypted and unauthorized.  Therefore, an adversary who wishes to harm the CubeSat, or harm another object using the CubeSat, may sniff a command packet to the satellite and control it. Dr. Bellardo has given us a set of requirements that the library should have.

@@

Our library can not use transfer large amount of data between home base and the satellite. AX.25 speed limits on data are rarely higher than 9,600 bits/s and are usually 1,200 bits/s. \cite{AX25} The satellite also does not return an acknowledgement packet after successful retrieving a packet. Therefore, we are restricted on which scheme to use for our crypto library. Another issue is the connection time with the CubeSat is at most 15 minutes an hour due to the satellite orbiting the Earth. Therefore, we cannot use schemes that require a constant connection with the satellite. 

@@

Our library should allow any user to have the option to encrypt or authenticate their packets. It should have 3 functions: No security, one way authentication, and authenticated encryption. Using the diagram on the next page is how Dr. Bellardo described how we should encrypt and authenticate. We were told to only encrypt the data portion of the packet, and only authenticate the IPv4 and UDP headers along with the data.

@@

We began our research by looking for current satellite encryption. We found a paper on AES (Advanced Encryption Standard) with LDPC (Low Density Parity Check Code) in order to design a secure and reliable error correction method. \cite{SEEC} We also found that stream ciphers lead to serious problems if used incorrectly for satellite applications. \cite{streamproblems} We discovered someone else's work to authenticate IP protocol. \cite{IPProtocol} In order to meet the low overhead requirement we found a low cost one-way HMAC proposal for a RFID system. \cite{HMACRFID} With all of this information, we needed a light weight software library for encryption to use. 

@@

The sign function takes in a 32-byte key \cite{NaClSiteAuth} and variable-length IPv4 packet to output a signed IPv4 packet which has a 32-byte tag \cite{NaClSiteAuth} inserted in the head of the data portion. \footnote{Because we did get to perform live testing, we are unsure if this insertion breaks the IPv4 system. An alternative process for inserting the tag is possible.} The verify function takes a signed IPv4 packet and removes the inserted tag from the head of the data portion. Verification is then performed on the reconstructed packet by generating a new tag to compare with the provided tag. Based on the source files, the comparison in TweetNaCl is done by a constant-time string comparison function to avoid creating side-channels. If the packet verifies, the function outputs the new size of the reconstructed packet. Otherwise, it outputs -1 as ⊥.

@@

Authenticated encryption in LiteCrypto makes use of the authentication and encryption functions discussed above. To encrypt a packet, we first perform our encryption scheme then our authentication scheme. We have ultimately inserted 56 bytes into the IPv4 packet: 32 bytes from authentication tag and 24 bytes from encryption nonce. To decrypt, we first attempt to verify the packet. If the packet verifies, we perform our decryption scheme and output the decrypted packet without the 56 bytes originally inserted; otherwise, -1 is outputted as ⊥. Our encrypt-sign and verify-decrypt schemes achieve authenticated encryption by never decrypting a non-authenticated packet.

>>>>

\vfill  %in combination with \newpage this forces the abstract to the bottom of the page
\begin{abstract}
As satellite communication becomes more accessible with the introduction of CubeSats, the need for authenticated and encrypted communication become necessary to protect against attackers. We have developed a lightweight, open-source cryptographic library suitable for satellites, specifically CubeSats, based on the NaCl and TweetNaCl libraries. The library, LiteCrypto, includes authentication, encryption, and authenticated encryption for IPv4 packets under symmetric keys.

@@

Dr. Bellardo has discussed with our team that the future of CubeSat is to allow them to move in space. However, their current communications from home base to the satellite is unencrypted and unauthorized.  Therefore, an adversary who wishes to harm the CubeSat, or harm another object using the CubeSat, may sniff a command packet to the satellite and control it. Dr. Bellardo has given us a set of requirements that the library should have.

@@

Our library can not transfer large amount of data between home base and the satellite. AX.25 speed limits on data are rarely higher than 9,600 bits/s and are usually 1,200 bits/s. \cite{AX25} The satellite also does not return an acknowledgement packet after successful retrieving a packet. Therefore, we are restricted on which scheme to use for our crypto library. Another issue is that the connection time with the CubeSat is at most 15 minutes an hour due to the satellite orbiting the Earth. Therefore, we cannot use schemes that require a constant connection with the satellite. 

@@

Our library should allow any user to have the option to encrypt or authenticate their packets. It should have 3 functions: No security, one way authentication, and authenticated encryption. The diagram on the next page is how Dr. Bellardo described how we should encrypt and authenticate. We were told to only encrypt the data portion of the packet, and only authenticate the IPv4 and UDP headers along with the data.

@@

We began our research by looking for current satellite encryption. We found a paper on AES (Advanced Encryption Standard) with LDPC (Low Density Parity Check Code) in order to design a secure and reliable error correction method. \cite{SEEC} We also found that stream ciphers lead to serious problems if used incorrectly for satellite applications. \cite{streamproblems} We discovered someone else's work to authenticate IP protocol. \cite{IPProtocol} In order to meet the low overhead requirement, we found a low cost one-way HMAC proposal for a RFID system. \cite{HMACRFID} With all of this information, we needed a lightweight software library for encryption to use. 

@@

The sign function takes in a 32-byte key \cite{NaClSiteAuth} and variable-length IPv4 packet to output a signed IPv4 packet which has a 32-byte tag \cite{NaClSiteAuth} inserted in the head of the data portion. \footnote{Because we did get to perform live testing, we are unsure if this insertion breaks the IPv4 system. An alternative process for inserting the tag is possible.} The verify function takes a signed IPv4 packet and removes the inserted tag from the head of the data portion. Verification is then performed on the reconstructed packet by generating a new tag to compare with the provided tag. Based on the source files, the comparison in TweetNaCl is done by a constant-time string comparison function to avoid creating side-channels. If the packet verifies, the function outputs the new size of the reconstructed packet. Otherwise, it outputs -1 as $\bot$.

@@

Authenticated encryption in LiteCrypto makes use of the authentication and encryption functions discussed above. To encrypt a packet, we first perform our encryption scheme then our authentication scheme. We have ultimately inserted 56 bytes into the IPv4 packet: 32 bytes from authentication tag and 24 bytes from encryption nonce. To decrypt, we first attempt to verify the packet. If the packet verifies, we perform our decryption scheme and output the decrypted packet without the 56 bytes originally inserted; otherwise, -1 is outputted as $\bot$. Our encrypt-sign and verify-decrypt schemes achieve authenticated encryption by never decrypting a non-authenticated packet.
